E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-06 paper.tex
slight formatting changes done
added biblio
fixing more shtuff
lil adds

	\section{Introduction}
	\input{introduction}

@@

	\subsection{Math Equations}
	You may want to display math equations in three distinct styles:
	inline, numbered or non-numbered display.  Each of
	the three are discussed in the next sections.

	\subsubsection{Inline (In-text) Equations}
	A formula that appears in the running text is called an
	inline or in-text formula.  It is produced by the
	\textbf{math} environment, which can be
	invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
	construction or with the short form \texttt{\$. . .\$}. You
	can use any of the symbols and structures,
	from $\alpha$ to $\omega$, available in
	\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
	few examples of in-text equations in context. Notice how
	this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
	set here in in-line math style, looks slightly different when
	set in display style.  (See next section).

	\subsubsection{Display Equations}
	A numbered display equation -- one set off by vertical space
	from the text and centered horizontally -- is produced
	by the \textbf{equation} environment. An unnumbered display
	equation is produced by the \textbf{displaymath} environment.

	Again, in either environment, you can use any of the symbols
	and structures available in \LaTeX; this section will just
	give a couple of examples of display equations in context.
	First, consider the equation, shown as an inline equation above:
	\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
	Notice how it is formatted somewhat differently in
	the \textbf{displaymath}
	environment.  Now, we'll enter an unnumbered equation:
	\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
	and follow it with another numbered equation:
	\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
	just to demonstrate \LaTeX's able handling of numbering.

	\subsection{Citations}
	Citations to articles \cite{bowman:reasoning,
		clark:pct, braams:babel, herlihy:methodology},
	conference proceedings \cite{clark:pct} or
	books \cite{salas:calculus, Lamport:LaTeX} listed
	in the Bibliography section of your
	article will occur throughout the text of your article.
	You should use BibTeX to automatically produce this bibliography;
	you simply need to insert one of several citation commands with
	a key of the item cited in the proper location in
	the \texttt{.tex} file \cite{Lamport:LaTeX}.
	The key is a short reference you invent to uniquely
	identify each work; in this sample document, the key is
	the first author's surname and a
	word from the title.  This identifying key is included
	with each item in the \texttt{.bib} file for your article.

	The details of the construction of the \texttt{.bib} file
	are beyond the scope of this sample document, but more
	information can be found in the \textit{Author's Guide},
	and exhaustive details in the \textit{\LaTeX\ User's
		Guide}\cite{Lamport:LaTeX}.

	This article shows only the plainest form
	of the citation command, using \texttt{{\char'134}cite}.
	This is what is stipulated in the SIGS style specifications.
	No other citation format is endorsed or supported.

@@

	%
	% The following two commands are all you need in the
	% initial runs of your .tex file to
	% produce the bibliography for the citations in your paper.
	\bibliographystyle{abbrv}
	\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
	% You must have a proper ".bib" file
	%  and remember to run:
	% latex bibtex latex latex
	% to resolve all references
	%
	% ACM needs 'a single self-contained file'!
	%
	%APPENDICES are optional
	%\balancecolumns
	\appendix
	%Appendix A
	\section{Headings in Appendices}
	The rules about hierarchical headings discussed above for
	the body of the article are different in the appendices.
	In the \textbf{appendix} environment, the command
	\textbf{section} is used to
	indicate the start of each Appendix, with alphabetic order
	designation (i.e. the first is A, the second B, etc.) and
	a title (if you include one).  So, if you need
	hierarchical structure
	\textit{within} an Appendix, start with \textbf{subsection} as the
	highest level. Here is an outline of the body of this
	document in Appendix-appropriate form:
	\subsection{Introduction}
	\subsection{The Body of the Paper}
	\subsubsection{Type Changes and  Special Characters}
	\subsubsection{Math Equations}
	\paragraph{Inline (In-text) Equations}
	\paragraph{Display Equations}
	\subsubsection{Citations}
	\subsubsection{Tables}
	\subsubsection{Figures}
	\subsubsection{Theorem-like Constructs}
	\subsubsection*{A Caveat for the \TeX\ Expert}
	\subsection{Conclusions}
	\subsection{Acknowledgments}
	\subsection{Additional Authors}
	This section is inserted by \LaTeX; you do not insert it.
	You just add the names and information in the
	\texttt{{\char'134}additionalauthors} command at the start
	of the document.
	\subsection{References}
	Generated by bibtex from your ~.bib file.  Run latex,
	then bibtex, then latex twice (to resolve references)
	to create the ~.bbl file.  Insert that ~.bbl file into
	the .tex source file and comment out
	the command \texttt{{\char'134}thebibliography}.
	% This next section command marks the start of
	% Appendix B, and does not continue the present hierarchy
	\section{More Help for the Hardy}
	The sig-alternate.cls file itself is chock-full of succinct
	and helpful comments.  If you consider yourself a moderately
	experienced to expert user of \LaTeX, you may find reading
	it useful but please remember not to change it.
	%\balancecolumns % GM June 2007
	% That's all folks!
\end{document}

>>>>

	\input{introduction}

@@

@@

	%
	% The following two commands are all you need in the
	% initial runs of your .tex file to
	% produce the bibliography for the citations in your paper.
	\bibliographystyle{abbrv}
	\bibliography{biblio}  
	% You must have a proper ".bib" file
	%  and remember to run:
	% latex bibtex latex latex
	% to resolve all references
	%
	% ACM needs 'a single self-contained file'!
	%
	%APPENDICES are optional
	%\balancecolumns
	\appendix
	%Appendix A
	\section{Headings in Appendices}
	The rules about hierarchical headings discussed above for
	the body of the article are different in the appendices.
	In the \textbf{appendix} environment, the command
	\textbf{section} is used to
	indicate the start of each Appendix, with alphabetic order
	designation (i.e. the first is A, the second B, etc.) and
	a title (if you include one).  So, if you need
	hierarchical structure
	\textit{within} an Appendix, start with \textbf{subsection} as the
	highest level. Here is an outline of the body of this
	document in Appendix-appropriate form:
	\subsection{Introduction}
	\subsection{The Body of the Paper}
	\subsubsection{Type Changes and  Special Characters}
	\subsubsection{Math Equations}
	\paragraph{Inline (In-text) Equations}
	\paragraph{Display Equations}
	\subsubsection{Citations}
	\subsubsection{Tables}
	\subsubsection{Figures}
	\subsubsection{Theorem-like Constructs}
	\subsubsection*{A Caveat for the \TeX\ Expert}
	\subsection{Conclusions}
	\subsection{Acknowledgments}
	\subsection{Additional Authors}
	This section is inserted by \LaTeX; you do not insert it.
	You just add the names and information in the
	\texttt{{\char'134}additionalauthors} command at the start
	of the document.
	\subsection{References}
	Generated by bibtex from your ~.bib file.  Run latex,
	then bibtex, then latex twice (to resolve references)
	to create the ~.bbl file.  Insert that ~.bbl file into
	the .tex source file and comment out
	the command \texttt{{\char'134}thebibliography}.
	% This next section command marks the start of
	% Appendix B, and does not continue the present hierarchy
	\section{More Help for the Hardy}
	The sig-alternate.cls file itself is chock-full of succinct
	and helpful comments.  If you consider yourself a moderately
	experienced to expert user of \LaTeX, you may find reading
	it useful but please remember not to change it.
	%\balancecolumns % GM June 2007
	% That's all folks!
\end{document}
